cardinalR: Generating interesting high-dimensional data structures

### 2025-05-01 paper-cardinalR.Rmd
Added projection for S-curve data

>>>>

```{r data-scurve, echo=TRUE}
scurve <- gen_scurve(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(scurve)
```

```{r scurve-proj1}
scaled_data <- scale_data_manual(scurve)

scurve_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r scurve-proj2}

scurve_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r scurve-proj3}

scurve_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-scurve-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurve` data."}
#| fig-width: 15
#| fig-height: 5

scurve_proj1 + scurve_proj2 + scurve_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-scurvehole, echo=TRUE}
scurvehole <- gen_scurvehole(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(scurvehole)
```

```{r scurvehole-proj1}
scaled_data <- scale_data_manual(scurvehole)

scurvehole_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r scurvehole-proj2}

scurvehole_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r scurvehole-proj3}

scurvehole_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-scurvehole-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurvehole` data."}
#| fig-width: 15
#| fig-height: 5

scurvehole_proj1 + scurvehole_proj2 + scurvehole_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```
